\section{Damian Zaremba}\label{damian-zaremba}

TL;DR I like interesting problems, at scale, mostly involving
networking.

((Systems + Networking) + Bussiness requirements = Positive bussiness
impact) == \textless{}3

\subsection{Summary}\label{summary}

Linux/network focused sysadmin constantly looking to improve service and
run at the edge of technology.

Passionate about networking, architecture, solution design, automation,
testing, Linux, open source, micro optimisations, monitoring, metrics
and graphing.

Driven to impact change where required and deliver things done
efficiently and effectively.

\subsection{Employment History}\label{employment-history}

\subsubsection{Booking.com - Network
Engineer}\label{booking.com---network-engineer}

\emph{September 2016 - Present}

Working in network engineering, dealing with infrastructure related to
running \href{https://stat.ripe.net/AS43996}{AS43996} /
\href{https://stat.ripe.net/AS202196}{AS202196}.

Also manage and develop internal systems related to provisioning,
monitoring and managing network infrastructure across the globe.

\subsubsection{TravelJigsaw Limited (Rentalcars.com) - Principal
Security
Engineer}\label{traveljigsaw-limited-rentalcars.com---principal-security-engineer}

\emph{November 2015 - September 2016}

Focused on improving all technical aspects of the security landscape.

Worked closely with Legal, Finance, Technology and Security teams in the
business to deliver security objectives.

A number of large undertakings were completed successfully including:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Achieving a \textasciitilde{}65\% reduction in external facing
  vulnerabilities, while observing a \textasciitilde{}44\% increase in
  assets.
\item
  Deploying an OpenLDAP topology, synced with Active Directory entries,
  using SASL to hand off password authentication
\item
  Deploying an internal certificate authority and root certificates
  (ca-bundle + JKS files) to 800+ servers
\item
  Developing tooling in Puppet for firewall rule management and deployed
  restrictive Iptables rules to 800+ servers
\item
  Deploying OpenLDAP using SSSD \& pam\_access to 800+ servers for
  centralised authentication and access control
\item
  Building tooling around Nexpose, Serverspec \& Test Kitchen for
  integration into a CI pipeline
\item
  Deploying an OSSEC setup to 800+ servers
\item
  Implementing internal vulnerability scanning of \textasciitilde{}2000
  assets.
\item
  Rebuilding the entire PCI DSS environment with minimal business impact
  and 100\% removal of vulnerabilities, including conformance to PCI DSS
  (level 2, with external QSA assessment)
\item
  Developing CSP/HPKP functionality and servlet filters for external
  facing applications, including reporting functionality to assess the
  impact of policy/filter changes
\item
  Developing tooling for automated server patching (including staged
  rollouts + reporting)
\item
  Developing tooling for rotating encryption keys on 10+ million data
  entries in a fast and minimally impactful manner
\item
  Deploying a horizontally scalable (Anycast + Resilient ECMP based)
  load balancing implementation using HAProxy to support migrating all
  external traffic to use TLS
\end{itemize}

More day to day operational items included:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Introducing hiera-eyaml (using the GPG backend) and node\_encrypt into
  Puppet (3.x), for improved configuration secrets handling
\item
  Deploying SELinux in targeted mode to all `critical infrastructure'
  (including in PCI/PII zones and core infrastructure)
\item
  Developing security tooling with appropriate access controls for
  common activities such as managing OSSEC alerts, reporting on user
  access and changing on-call settings.
\item
  Developing Python tooling for handling inventory changes in `black
  box' security appliances
\item
  Developing Python tooling for streaming SIEM alerts off multiple
  closed `black box' security appliances into a single events stream,
  combined with OSSEC events
\item
  Working with vendors to PoC and implement security appliances,
  including deploying TAP (Arista 7150 based) infrastructure for data
  collection/aggregation
\item
  Providing expert level support to the architecture and engineering
  teams within the Technology department
\item
  Performing reviews on proposed solutions and technical aspects of
  legal contracts
\item
  Upgrading numerous server roles (including all core infrastructure) to
  CentOS 6.8 and Puppet 3.x
\item
  Providing security on-call coverage (for both SIEM alerts and as an
  escalation point for events)
\item
  Standardising firewall rules across multiple Juniper SRX clusters
\item
  Working with external and internal auditors to improve controls and
  ensure (SoX, PCI DSS, DPA, Privacy Shield) compliance
\item
  Developing tooling for server patching in a controlled manner,
  targeting both CentOS and VMWare ESXI (4.x / 5.x); Successfully
  upgraded 100+ VMWare hosts, 800+ CentOS 6.x servers
\item
  Developing abstractions in puppet for managing pam\_access and sudo
  (group) based access rules, with inheritance
\item
  Supported the Network team in implementing new internet infrastructure
  (routing policy, peering points, redundancy testing, design of
  firewall cluster connectivity to avoid L2 spans in transit layers,
  confederated BGP etc); this was the implementation of the solution
  previously designed (see the previous role)
\item
  Interviewing candidates for engineering and development roles
\item
  Drafting a roadmap and key milestones for security enhancements
\end{itemize}

\subsubsection{TravelJigsaw Limited (Rentalcars.com) - Technical
Architect}\label{traveljigsaw-limited-rentalcars.com---technical-architect}

\emph{June 2015 - November 2015}

As a founding member of the architecture team (team of 3), my initial
focus was a review of the core systems, potential contention/failure
points and a roadmap for core infrastructure.

The work was varied and included documenting/diagramming existing
systems, interviewing candidates for multiple roles (engineers, managers
\& contractors), providing expert support during service issues/solution
design, building software prototypes, working with the teams to
establish standards and designing new solutions.

A number of solutions were designed, many of which ended up in
production:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  A new internet connectivity segment, removing single providers/devices
  out of a critical path and improving scalability for the future; this
  established the first ASN and IP space directly held by the company
\item
  Route based injection for service discovery; a successful PoC and
  accepted for specific services. No wide rollout due to a lack of equal
  cost within the main access network
\item
  AWS direct connect for hybrid (test/development) environments; a
  successful PoC, now supporting multiple teams and production services
\item
  A new `event backbone' using Apache Flume and Kafka with custom
  consumers written in Java; a successful PoC handling millions of
  events a minute. This is now the standard way to transmit/consume
  events within the company and has 2 Kafka clusters deployed,
  publishing events into a diverse set of backends (ElasticSearch,
  MySQL, AppDynamics, HDFS, CSV files etc)
\end{itemize}

Other outcomes include:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  An 18-month roadmap/improvement plan for the network
\item
  Numerous risks identified within the technology landscape and
  prioritised for resolution with the engineering teams
\item
  Implementation of Bamboo for CI, including multiple example jobs and
  Java-based plugins
\item
  Implementation of Artifactory Pro for internal binary sharing
  (integrated into Bamboo and internal deployment systems)
\item
  Updated design for a multistage Clos architecture within the DCs
  (budgeted for completion Q4 2016)
\end{itemize}

Some areas of investigation were undertaken:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Impact of deploying Docker into Production; this was determined to be
  dependent on an equal cost network due to the impact of differential
  latencies between access segments on performance
\item
  Real(ish) time event analysis (using Parquet backed tables in Hadoop);
  the primary driver for this was to power a re-build of the internal
  A/B/n / MVT testing dashboards
\item
  Datacenter standardisation via logical (vRF) rather than physical role
  separation
\end{itemize}

\subsubsection{TravelJigsaw Limited (Rentalcars.com) - Linux Systems
Administrator}\label{traveljigsaw-limited-rentalcars.com---linux-systems-administrator}

\emph{February 2014 - June 2015}

Working in a team of 3 sysadmins maintaining, tuning and updating the
1k+ servers that make up the infrastructure.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Managed/deployed a heterogeneous infrastructure consisting of bare
  metal rack mount and blade servers (HP/Dell) alongside VMWare ESX,
  KVM, Docker and EC2 based instances
\item
  Refactored a Puppet 2.x setup into a Puppet 3.x setup using the latest
  language standards and the principle of state convergence on the first
  run
\item
  Supported the internal tools written in Python/Ruby including the
  Django-based asset management tool
\item
  Provided out of hours support to the business via an on-call rota
\item
  Introduced CI to operations for RPM builds and puppet testing
\item
  Re-designed the core network to be a fabric based setup, based on a
  multi-stage Clos architecture
\item
  Coordinated with data centre and network teams to ensure changes are
  completed as required by the business
\item
  Deployed anti-virus scanning and DKIM signing of outbound messages
  using Exim routers to ensure external facing email meets
  validation/verification levels requested by the business
\item
  Developed multiple fabric based scripts for real-time auditing and
  remediation of servers (firmware versions, log file cleanup etc)
\item
  Built a PoC SaltStack deployment
\item
  Performed troubleshooting on multiple issues of PHP-FPM, Tomcat, Java
  7/8, Nginx, Apache \& F5 setups
\item
  Championed the use of upstream packages and versions of core software
\item
  Worked closely with development teams to test new software and build a
  path to production
\item
  Developed kickstart files and custom initrd files for server
  installation (including automated firmware updates)
\item
  Developed acceptance tests for hardware using PyUnit and Fabric
\item
  Interviewed candidates for junior sysadmin positions and devised
  training plans for them within the company
\item
  Devised tests for and interviewed candidates for senior engineering
  positions
\end{itemize}

A part of this role involved building the initial infrastructure for
Car+Driver (Rideways.com); a startup within the company. This was
accomplished using:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  AWS EC2/S3/RDS/Cloudfront/Cloudformation/ElastiCache
\item
  Python (troposphere) based CloudFormation generation
\item
  Python (boto) based deployment scripts, for CloudFormation and
  CodeDeploy
\item
  Packer + Puppet (masterless) based AMI creation
\item
  Github + Bamboo + Jira for CI/CD
\end{itemize}

\subsubsection{MUSIC Group - Software Engineer (RnD - Midas/Klark
Teknik)}\label{music-group---software-engineer-rnd---midasklark-teknik}

\emph{July 2013 - February 2014}

Working on new Midas/Klark Teknik products and supporting internal R\&D
infrastructure.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Deployed an isolated 3 node (2 HA controllers) OpenStack Havana set-up
  using NetApp ONTAP storage.
\item
  Designed and implemented a small `collapsed-core' network - using
  Cisco technologies
\item
  to provide an isolated R\&D network, inside an existing (insecure)
  corporate network.
\item
  Performed data recovery on R\&D servers/data and developed workarounds
  for internal services during a 4-month long global TECH service
  failure.
\item
  Developed a testing jig for boards using a raspberry PI with GPIO
  controlled relays, for automated boot loader re-programming and boot
  timing on changes.
\item
  Developed and implemented backup/restore procedure for critical data
  (source code, tickets, build configurations).
\item
  Rearchitected the current 2 server setup (unmonitored, running on raid
  0, constrained by disk/CPU) into a 3 node OpenStack setup and
  re-purposed older servers (removed from service during a transition
  from CVS to Git) as disposable build agents.
\item
  Implemented configuration management (Puppet), service orchestration
  (Salt stack) and service/change monitoring (Icinga/Rancid).
\item
  Reduced build times (14 hours to 40min) and implemented a new strategy
  for multi-component builds.
\item
  Drove continuous deployment methodologies into new product design
\item
  Designed a framework and strategy for increasing confidence in code
  and speeding up the release cycle.
\item
  Developed software against x86, STM32, and ARM-based platforms,
  including acting as the control plane for embedded switches/FPGAs/DSPs
\item
  Exposure to proprietary binary based communications protocols and
  their pitfalls vs open, standards-based communications protocols and
  their benefits
\item
  Performed maintenance on LFS and Ltib systems for building products
\item
  Debugged and rectified issues in C++/Python/Perl code and
  shell/Sed/Awk scripting
\item
  Investigated web technologies, updating/deployment methodologies, RFB
  reverse tunnelling, SELinux, and performance analysis/containment.
\item
  Utilised kernel features to enhance new products (control groups,
  SELinux, nftables)
\item
  Documented processes for developers (board reprogramming/power
  up/hardware interfaces)
\item
  Ported numerous internal applications from x86 to ARM
\item
  Managed Atlassian developer tools (Jira, Stash, Bamboo, Fisheye)
\end{itemize}

\subsubsection{MUSIC Group - Systems Engineer (Global Enterprise
Engineering)}\label{music-group---systems-engineer-global-enterprise-engineering}

\emph{October 2012 - July 2013}

Supporting world-recognised pro audio brands such as MIDAS, Klark
Teknik, Turbosound, Behringer, and Bugera.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Mixed Operations/engineering role covering all levels of the
  infrastructure.
\item
  Managed a complex heterogeneous infrastructure based upon VMware.
\item
  Implementing service monitoring and metric collection systems (MRTG,
  Smokeping, Icinga, Graphite, PRTG).
\item
  Troubleshooting layer 2/3 network issues across multiple sites
  (combination of P2P MPLS links (L2 \& 3), MPLS cloud and GRE tunnels
  connected via a mix of OSPF and static routes).
\item
  Developed custom integration (Icinga to Service Desk for ticketing,
  Pager duty acknowledgements to Icinga acknowledgements for alerts),
  plugins (VMware hardware checking, Oracle ESSO transaction level
  checking) and templates (network devices, server roles etc.) for
  monitoring systems.
\item
  Developed a custom roster system based around email DL's for Openfire,
  based on business requirements.
\item
  Developed numerous scripts for auditing and policy enforcement
  purposes.
\item
  Automated manual tasks to increase reliability.
\item
  Maintained bin log based replication on multiple MySQL clusters.
\item
  Dealt with multiple outages relating to VMware/DNS/Network/Disk
  availability.
\item
  Developed strategies for operating system deployment and management
  globally (primarily Ubuntu).
\item
  Packaged and maintained numerous pieces of software into DEB and RPM
  files for distribution.
\item
  Developed strategies for enforcing change control within a
  configuration management set-up (gating/testing change sets, peer
  review, environment isolation).
\item
  Diagnosed multiple issues with an Oracle ESSO deployment.
\item
  Implemented RANCID based backups for network device configurations.
\item
  Implemented LLDP/CDP based network topology diagraming for the
  discovery of devices within an unknown network.
\item
  Supported the implementation of a new network design (3 DCs, existing
  offices converted to leased lines, EIGRP backbone, OSFP in office, BGP
  to the internet and between sites)
\end{itemize}

\subsubsection{Sub 6 Limited - Lead Systems
Administrator}\label{sub-6-limited---lead-systems-administrator}

\emph{October 2011 - August 2012}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Lead the system administration/management side of the UK/US based
  managed hosting companies.
\item
  Handled escalated issues, complex solutions, monitoring and reporting
  requirements.
\item
  Integrated multiple services into the asset management system to cut
  down on manual steps and automate the process.
\item
  Introduced continuous integration into the development workflow.
\item
  Rolled out Puppet for configuration management.
\item
  Handled configuration of the switched network.
\item
  Designed and implemented a network topology to `in-house' all UK DC
  networking
\item
  Rolled out LDAP and Radius for centralised authentication.
\item
  Developed custom features for Kayako and WHMCS.
\item
  Introduced Graphite and exposed monitoring metrics to clients.
\item
  Increased security across the entire platform (PBX, DNS, Billing,
  client servers).
\item
  Implemented rolling password changes on a twice weekly basis.
\item
  Designed and developed an in-house (customer facing) IP-based FTP
  access manager.
\item
  Designed and developed a bespoke (customer facing) version manager for
  4 x PHP versions.
\item
  Developed a gatekeeper service to display holding pages for clients
  during a datacenter move.
\item
  Developed numerous custom solutions for clients.
\end{itemize}

\subsubsection{AllGamer, LLC - Freelance systems administrator and
developer}\label{allgamer-llc---freelance-systems-administrator-and-developer}

\emph{November 2010 - September 2011}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Advised on system automation and maintenance.
\item
  Integrated systems into the CRM.
\item
  Assisted in service issue diagnostic and resolution.
\item
  Assisted on service and metric monitoring (Nagios, SNMP, RRDTool,
  SmokePing).
\item
  Development of community tools.
\item
  Programming of system utilities.
\end{itemize}

\subsubsection{Calyx - Unix/Linux systems
administrator}\label{calyx---unixlinux-systems-administrator}

\emph{April 2011 - May 2011 (contract)}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Responsible for an RHEL5 RHCS set-up.
\item
  Managed Apache, Tomcat, JBos, Oracle 10G, MySQL.
\item
  Provided on-call support.
\item
  Provided users support in a third line capacity.
\item
  Successfully identified and resolved memory leaks within the
  application servers.
\item
  Managed Xen and Citrix XenServer deployments.
\item
  Debugged tomcat logs to identify root causes of application issues.
\item
  Implemented process monitoring of background workers to ensure a
  responsive application.
\end{itemize}

\subsubsection{CloudFlux - Systems
Engineer/Developer}\label{cloudflux---systems-engineerdeveloper}

\emph{October 2010 - May 2011}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Implemented service monitoring and performance graphing.
\item
  Developed a management framework.
\item
  Automated management tasks.
\item
  Managed backups of multiple servers.
\item
  Provided users support in a second/third line capacity.
\item
  Migrated from Xen to KVM.
\item
  Managed a KVM based virtual host.
\item
  Migration of SVN to Git.
\end{itemize}

\subsubsection{UKFast - Linux Engineer}\label{ukfast---linux-engineer}

\emph{February 2010 - October 2010}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Provided support in a 3rd line capacity.
\item
  Handled technical pre-sales and server set-up.
\item
  Maintained SLAs.
\item
  On-Call/Out of hours work.
\item
  Managing custom platforms, cPanel, Plesk, IIS, Apache, HAProxy, Nginx,
  LVS.
\item
  Configured and managed multiple Database and File replication
  solutions.
\item
  Dealt with multiple, geographically redundant sites with solutions
  spanning across 2 or more.
\item
  Handled network and power issues on a datacenter level.
\item
  Solely responsible for investigating and resolving alerts during out
  of hours.
\end{itemize}

\subsubsection{Freelancer: Architecture, Infrastructure, Linux
Deployment, Network Design, Software
Development}\label{freelancer-architecture-infrastructure-linux-deployment-network-design-software-development}

\emph{November 2008 - Current}

End to end management and design of infrastructure, heavily Linux and
Network focused.

Provide software development as required in Python (including Django),
Perl, PHP, C++ \& Ruby. Primary focus on extending open source solutions
and API services.

Previously deployed Linux solutions at edge and core, covering small
offices up to multi-datacenter setups. Solutions including PXE
(kickstart/preseed/Cobbler), Katello, Puppet, SaltStack, asset tracking,
lifecycle management, testing, custom Linux distributions and bespoke
auditing tools.

Designed networks to specification (cost or functionality), familiar
with large layer 2/3 deployments including STP, DTP, LACP protocols,
VLAN tagging, trunking, layer 2 protections (ARP, DHCP, BPDU guard),
static routing, dynamic routing (RIP, OSPF, EIGRP, BGP), MPLS (L2 and L3
VPNs, LSPs), QOS, ASA firewalls, ACL management, redundancy, performance
optimisation, asynchronous routing, remote troubleshooting, issue
diagnostics (layer 1-8) and vendor interaction/management (global).

Re-designed and migrated multiple data centre architectures for hosting
providers and global companies including coordination with on-site
resources for physical relocation, design constraints, and
implementation of redundant core and distribution network services,
designing single points of failure out, isolating management
connectivity into segregated failure domains (physically, up to a
separate BGP mix with different routes), the design of troubleshooting
tools for helpdesk staff, auditing equipment, implementation of off-site
backup arrangements, low-level migration tools (redirection of network
traffic to holding servers, DDOS protection, distributed caching,
automated route adjustment tools, automated firewall rule distribution
tools), power usage profiling and cost reduction.

\subsection{Volunteering experience}\label{volunteering-experience}

\subsubsection{FOSDEM volunteer}\label{fosdem-volunteer}

\emph{January 31st 2014 - 2nd February 2014}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Assisted with the build out for FOSDEM, prior to the event.
\item
  Assisted with the clean up of the ULB in Brussels, post FOSDEM.
\item
  Assisted with any misc tasks as required during the conference, based
  on organiser requirements.
\item
  Assisted with the initial video editing for Saturday's raw footage.
\item
  Moderated multiple talks (keynotes/main tracks) in the Jason building
  (1400 seat capacity).
\item
  Worked with a multinational team of volunteers (50+) to help deliver
  512 talks over 22 rooms in 2 days.
\end{itemize}

\subsubsection{The Scout Association}\label{the-scout-association}

\emph{December 2006 - January 2014}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Assistant Scout Leader.
\item
  Assist with program creation and delivery.
\item
  Teach new skills.
\item
  Perform building and equipment maintenance.
\item
  Ensure meetings take place safely.
\item
  Activity instructor for climbing.
\item
  Completed training for first aid, climbing, safeguarding and
  leadership
\item
  Assist local camp sites, district, county, and groups at large events.
\end{itemize}

\subsection{Professional certifications
(current)}\label{professional-certifications-current}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Red Hat Certified Engineer - 150-017-028
\item
  Red Hat Certified System Administrator - 150-017-028
\end{itemize}

\subsection{Misc}\label{misc}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  UK passport/driving licence
\item
  Available out of hours
\item
  Based in Amsterdam, Netherlands
\item
  References available upon request
\end{itemize}

\subsection{See Also}\label{see-also}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{https://github.com/damianzaremba}{GitHub} - damianzaremba
\item
  \href{http://last.fm/user/damianzaremba4}{Last.fm} - damianzaremba4
\item
  \href{http://uk.linkedin.com/in/damianzaremba}{LinkedIn} -
  damianzaremba
\item
  \href{http://damianzaremba.co.uk}{Website} - damianzaremba.co.uk
\end{itemize}
